PK object batch mode trial

### 2023-06-13 data-raw/batchMode_trial_gpm.Rmd
Adapted coef() function using data groups and started working on predict(), which calls coef()

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch
library(tidyverse)
library(here)
```

@@

```{r data_loading}
cvt %>% names()

cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442" &
                       subjects.species_harmonized %in% "rat")

@@

```{r}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = "L-BFGS-B") +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk <- preprocess_data(my_pk)

my_pk <- data_info(my_pk)

my_pk <- prefit(my_pk) 
# I get a warning here 
# "In med_y - pred : "
# "longer object length is not a multiple of shorter object length"

my_pk <- fit(my_pk)

pk_results <- coef(my_pk)

predict(my_pk) # Doesn't run rn for some reason
pred_results <- predict(my_pk)

plot_results <- plot(my_pk)
print(plot_results)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch

@@

The first step is understanding how to work with a single DTXSID + Species combination.
Once we know how to do this, it will be easier to apply it to (potentially)
a list of these objects in a vectorized fashion.
Here I subset the `cvt` object and use that as my working data.

```{r data_loading}
# There are 103 unique chemicals in this object
cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>%
  unique() %>%
  length()

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")

@@

Next, I want to follow the steps required for the particular analysis I would like.
In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
I do not scale the time or log-transform the concentration values.
Since I would like to do a "Pooled" analysis,
I set the `error_group = vars(Chemical, Species)`.

```{r single_fit}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
                                     subjects.species_harmonized))

my_pk <- do_preprocess(my_pk)

my_pk <- do_data_info(my_pk) 
# summarizes error (Returning more or less than 1 row per summarize)

my_pk <- do_prefit(my_pk)

my_pk <- do_fit(my_pk)
```

Batch mode works now I need to write a function that recapitulates `coef()` method

```{r coef_function_remake}
# A list of each fit model with the estimated parameters for that model
pk_results <- coef(my_pk) # NAs are printed

my_coefs_test <- my_pk$fit |>
  ungroup() |>
  tidyr::unnest(cols = fit) |>
  tidyr::unite(sigma, starts_with("sigma_"),
        na.rm = TRUE) |>
  group_split(method)

my_coef <- function(obj,
                    data_group = NULL,
                    ...) {
  # Check fit status
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)

  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted

  # Assign data groups to variable
  if (is.null(data_group)) data_group <- obj$data_group

  fit_coef <- obj$fit |>
    dplyr::ungroup() |>
    tidyr::unnest(cols = fit) |>
    tidyr::unite(sigma, starts_with("sigma_"),
                 na.rm = TRUE)# |>
    # dplyr::group_split(method)

  # method_names <- purrr::map(fit_coef,
  #     \(x) unique(x$method)) |>
  #   unlist()
  # 
  # names(fit_coef) <- method_names

  return(fit_coef)
}

my_coefs <- my_coef(my_pk)

```{r predict_method_remake}
pred_results <- predict(my_pk) # Error about missing parameters

my_test_data <- my_pk$data

my_test_data %>%
  group_by(!!!my_pk$data_group) %>%
  dplyr::select(all_of(c("Time", "Time.Units", "Dose", "Route", "Media"))) %>%
  dplyr::left_join(my_coefs,
            relationship = "many-to-many") -> joined_test_data

# Testing not complete
joined_test_data %>%
  relocate(method, .before = model) %>%
  group_by(across(Chemical:model)) %>%
  nest(.key = "coefs") %>%
  rowwise() %>%
  dplyr::mutate(model_fun = my_pk$stat_model[[model]]$conc_fun,
                predicted_Value = do.call(model_fun,
                                          args = list(
                                            params = coefs,
                                            dose = Dose,
                                            time = Time,
                                            route = Route,
                                            medium = Media
                                          )),
  .after = model) %>%
  head()

my_predict <- function(obj,
                       newdata = NULL,
                       type = "conc",
                       exclude = TRUE,
                       use_scale_conc = FALSE) {
    # Check fit status
  check <- check_required_status(obj = obj,
                                 required_status = status_fit)

  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted

  if (is.null(newdata)) newdata <- obj$data
  newdata_ok <- check_newdata(newdata = newdata,
                              olddata = obj$data,
                              req_vars = c("Time",
                                           "Time.Units",
                                           "Dose",
                                           "Route",
                                           "Media"),
                              exclude = exclude)

    #scale time if needed
  if (!("Time_trans" %in% names(newdata))){
  newdata$Time_trans <- convert_time(x = newdata$Time,
                                     from = newdata$Time.Units,
                                     to = obj$scales$time$new_units)
  }

  #apply transformations if so specified
  conc_scale <- conc_scale_use(obj = obj,
                               use_scale_conc = use_scale_conc)

}

```{r}
plot_results <- plot(my_pk)
